---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English - Part 2"
author: Martin Schweinberger
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: word_document
---

# Introduction{-}

This document shows an analysis of adjective amplification in Hong Kong, Indian , and Philippine English based on the respective components of the International Corpus of English (ICE).  

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

## Preparation{-}

In a first step, the session is prepared by clearing the work space, setting options, activating packages and functions, as well as loading relevant functions.

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# load packages
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
library(here)
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)   
```

## Load data{-}

```{r amphkpie_02_03, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- base::readRDS(file = here::here("data/editdata", "iceamp_04_clean.rda"))
# inspect
head(ice)
```

## Clean data

Factorize predictors and scale frequency

```{r amphkpie_02_05, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  select(-Id, -Correction, -SpeechUnit, -SpeechUnitCount, -PreContext, -Token, -L1, 
         -PostContext, -PreContextLong, -Amplified, -Nationality, -OtherLanguages, -Birthplace) %>%
  dplyr::mutate(Emotionality = ifelse(Emotionality == "PositiveEmotional", "Positive",
                               ifelse(Emotionality == "NonEmotional", "Neutral", "Negative")),
                Emotionality = factor(Emotionality, levels = c("Negative", "Neutral", "Positive")),
                Frequency = as.vector(scale(Frequency)),
                Gender = factor(Gender),
                EducationLevel = factor(EducationLevel),
                Priming = factor(Priming),
                Emotionality = factor(Emotionality),
                Function = factor(Function),
                Ethnicity = factor(Ethnicity),
                SemanticCategory = factor(SemanticCategory),
                Speaker = paste0(File, "$", Speaker)) %>%
  select(-File, -WordCount)
str(ice)
```

Determine adjective frequency

```{r amphkpie_02_07, echo=T, eval = T, message=FALSE, warning=FALSE}
fadj <- names(table(ice$Adjective))[which(table(ice$Adjective) > 15)]
fadj
```

Determine variant frequency

```{r amphkpie_02_09, echo=T, eval = T, message=FALSE, warning=FALSE}
famp <- names(table(ice$Variant))[which(table(ice$Variant) > 50)]
famp
```
Collapse infrequent adjectives and amplifiers

```{r amphkpie_02_11, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(Adjective = ifelse(Adjective %in% fadj, Adjective, "other"),
         Variant = ifelse(Variant %in% famp, Variant, "other"),
         Adjective = factor(Adjective),
         Variant = factor(Variant)) %>%
  group_by(Corpus) %>%
  mutate(Frequency = scale(Frequency)[,1])
str(ice)
```

## Data inspection{-}

Visualize Variant by Corpus and Age

```{r amphkpie_02_13, echo=T, eval = T, message=FALSE, warning=FALSE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) + 
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25"))
ggsave(file = 
           here::here("images", "VariantAgeCorpus.png"),
         height = 4,  width = 6, dpi = 320)
  
```

Visualize Variant by Corpus and Age and Function

```{r amphkpie_02_15, echo=T, eval = T, message=FALSE, warning=FALSE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant, Function) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age, Function) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus), rows=vars(Function)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) +  
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) 
ggsave(file = here::here("images", "VariantAgeCorpusFunction.png"),
         height = 4,  width = 6, dpi = 320)
  
```

# Analysis of ICE-PHI{-}

```{r amphkpie_02_17, echo=T, eval = T, message=FALSE, warning=FALSE}
phi <- ice %>%
  ungroup() %>%
  filter(Corpus == "ICE-PHI") %>%
  mutate(Age = factor(Age),
         Date = ifelse(Date == "1991"|Date == "1992", "Before1993", "After1998"),
         Date = factor(Date, levels = c("Before1993", "After1998")),
         Corpus = factor(Corpus),
         Speaker = factor(Speaker)) %>%
  droplevels()
# inspect
head(phi)
```

Find variables that cannot be tested

```{r amphkpie_02_19, echo=T, eval = T, message=FALSE, warning=FALSE}
l <- sapply(phi, function(x) is.factor(x))
m <- phi[, l]
ifelse(n <- sapply(m, function(x) length(levels(x))) == 1, "DROP", "NODROP")
```

Remove variables and NA

```{r amphkpie_02_21, echo=T, eval = T, message=FALSE, warning=FALSE}
nrow(phi)
phi_rfd <- phi %>%
  select(-Ethnicity, -Corpus, -EducationLevel, -Speaker) %>%
  na.omit()
nrow(phi_rfd)
```

## Random forest{-}

Identify variables to include in regression modeling.

```{r amphkpie_02_23, echo=T, eval = T, message=FALSE, warning=FALSE}
library(randomForest)
set.seed(2020082401)
rf_phi <- randomForest(Variant ~., data = phi_rfd, ntree=10000, proximity=TRUE, importance=TRUE)
# inspect rf results
rf_phi 
```

Plot out-of-bag error frequency

```{r amphkpie_02_25, echo=T, eval = T, message=FALSE, warning=FALSE}
# plot new precision/error rate
oob.error.data <- data.frame(
  Trees=rep(1:nrow(rf_phi$err.rate), times=5),
  Type=rep(c("OOB", "other", "really", "so", "very"), each=nrow(rf_phi$err.rate)),
  Error=c(rf_phi$err.rate[,"OOB"],
          rf_phi$err.rate[,"other"],
          rf_phi$err.rate[,"really"],
          rf_phi$err.rate[,"so"],
          rf_phi$err.rate[,"very"]))
ggplot(data=oob.error.data, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))
```

Check accuracy and improvement compared to base-line model

```{r amphkpie_02_27, echo=T, eval = T, message=FALSE, warning=FALSE}
# determine accuracy by prediction
library(caret)
# prediction
pnsrf <- predict(rf_phi, phi_rfd)
confusionMatrix(pnsrf, phi_rfd$Variant)
# calculate increase in prediction accuracy compared to base-line model
cm <- confusionMatrix(pnsrf, phi_rfd$Variant)
round(cm[3]$overall[[1]]/cm[3]$overall[[5]]*100, 2) - 100
```

Visualize variable importance

```{r amphkpie_02_31, echo=T, eval = T, message=FALSE, warning=FALSE}
varImpPlot(rf_phi, main = "", pch = 20, cex = 1.5)
png(here::here("images", "VarImp_IcePhi.png"),  width = 750, height = 500)
varImpPlot(rf_phi, main = "", pch = 20, cex = 1.25) 
dev.off()
```

### Extract RF-based predictions{-}


```{r amphkpie_02_33, echo=T, eval = T, message=FALSE, warning=FALSE}
pphi_rf <- predict(rf_phi, phi_rfd, type = "prob")
phi_pred <- cbind(phi_rfd, pphi_rf)
pphi <- phi_pred %>%
  gather(PredictedVariant, Probability, other:very)
# inspect
head(pphi)

```

Visualize predictions

```{r amphkpie_02_35, echo=T, eval = T, message=FALSE, warning=FALSE}
pphi %>%
  select(Age, Probability, Function, Gender, PredictedVariant) %>%
  mutate(Age = ifelse(Age == "16-25", 3, 
               ifelse(Age == "26-40", 2, 
               ifelse(Age == "41+", 1, Age)))) %>%
  group_by(Age, Function, Gender, PredictedVariant) %>%
  summarise(Probability = mean(Probability)) %>%
  ggplot(aes(x = Age, y = Probability, 
             group = PredictedVariant, color = PredictedVariant, linetype = PredictedVariant)) +
  geom_line() + 
  facet_grid(cols = vars(Gender), rows = vars(Function)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) +  
  scale_x_continuous(breaks = 1:3, 
                   labels = c("41+", "26-40", "16-25"))
ggsave(file = here::here("images", "VariantAgeFunction_Prob_Phi.png"),
         height = 5,  width = 6, dpi = 320)
```

## Regression analysis{-}

Prepare data

```{r amphkpie_02_37, echo=T, eval = T, message=FALSE, warning=FALSE}
pphi <- pphi %>%
  select(-Variant) %>%
  rename(Variant = PredictedVariant)
library(rms)
library(lme4)
library(car)
# generate models
m0.glm <- glm(Probability ~ 1, family = gaussian, data = pphi)
m0.glmer = glmer(Probability ~ 1 + (1|Adjective), data = pphi, family = "gaussian")
# extract aics
aic.m0.glmer <- AIC(logLik(m0.glmer))
aic.glm <- AIC(logLik(m0.glm))
aic.m0.glmer; aic.glm
```

### Model fitting{-}

Extract interactions

```{r amphkpie_02_39, echo=T, eval = T, message=FALSE, warning=FALSE}
# find all 2-way interactions
library(utils)
#colnames(pphi)
# define variables included in interactions
vars <- c("Variant", "Date", "Gender", "Age" , "Function", "Frequency", 
          "Priming", "Gradability", "SemanticCategory", "Emotionality")
# 2-way interactions (involving Variant)
intac_2way <- t(combn(vars, 2))
intac_2way <- intac_2way[which(intac_2way[,1] == "Variant"),]
int2w <- paste(intac_2way[,1], intac_2way[,2], sep = ":")
# 3-way interactions (involving Variant)
intac_3way <- t(combn(vars, 3))
intac_3way <- intac_3way[which(intac_3way[,1] == "Variant"),]
int3w <- paste(intac_3way[,1], intac_3way[,2], intac_3way[,3], sep = ":")
# combine vars, int2w and int3w
predictors <- paste(vars, int2w, int3w, sep = " + ", collapse = " + ")
# inspect
predictors
```

Create formula

```{r amphkpie_02_41, echo=T, eval = T, message=FALSE, warning=FALSE}
Formula <- formula(paste("Probability ~ ", "(1|Adjective/Variant) + ", predictors))
# full model with all variables
fm <- lmer(Formula, data = pphi)
# inspect
#fm
```

AIC-based automated model fitting

```{r amphkpie_02_43, echo=T, eval = T, message=FALSE, warning=FALSE}
library(lmerTest)
fixmodel <- lm(formula(fm, fixed.only = TRUE),
               data = eval(getCall(fm)$data))
lmerTest::step(fixmodel, k = log(nrow(pphi)))
```

Compare final minimal adequate model to intercept-only base-line model

```{r amphkpie_02_47, echo=T, eval = T, message=FALSE, warning=FALSE}
mf.glmer <- glmer(Probability ~  (1 | Adjective/Variant) + Variant + Date + Gender + Age + Function + 
    Priming + Gradability + Emotionality + Variant:Date + Variant:Gender + 
    Variant:Age + Variant:Function + Variant:Priming + Variant:Gradability + 
    Variant:Emotionality + Variant:Date:Gender + Variant:Date:Function + 
    Variant:Gender:Function + Variant:Gender:Priming, family = "gaussian", data = pphi)
# compare models                
anova(mf.glmer, m0.glmer, test = "Chi")
Anova(mf.glmer, type = "III", test = "Chi")
```

### Tabulate regression results{-}

```{r amphkpie_02_49, echo=T, eval = T, message=FALSE, warning=FALSE}
library(sjPlot)
tab_model(mf.glmer, p.val = "kr", show.df = TRUE)
```

### Visualize effects{-}

Plot effects
 
```{r amphkpie_02_51, echo=T, eval = T, message=FALSE, warning=FALSE}
library(effects)
png(here::here("images", "effectsfinalmodel.png"),  width = 960, height = 480) 
plot(allEffects(mf.glmer), type="response", ylim=c(0,1), grid=TRUE, 
     lines = list(col="black", lty = 1, confint=list(style="bars", col = "grey80")), ylab = "Probability")
dev.off()
#plot(allEffects(mf.glmer), type="response", ylim=c(0,1), grid=TRUE, 
#     lines = list(col="black", lty = 1, confint=list(style="bars", col = "grey80")), ylab = "Probability")
```

### Visualize individual effects{-}

Custom plot

```{r amphkpie_02_52, echo=T, eval = T, message=FALSE, warning=FALSE}
p_age_var <- plot_model(mf.glmer, type = "pred", terms = c("Age", "Variant"))
#p_age_var
```

Publishable plot

```{r amphkpie_02_53, echo=T, eval = T, message=FALSE, warning=FALSE}
ggplot(pphi, aes(Age, Probability)) +
  facet_grid(cols = vars(Variant)) +
  stat_summary(fun.y = mean, geom = "point", size = 1.5, color = "gray20") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", 
               width = 0.2, size = .5, color = "gray20") +
  coord_cartesian(ylim = c(-.1, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  labs(x = "Age", y = "Predicted probability") +
    scale_x_discrete(limits = rev(levels(pphi$Age)))
ggsave(here::here("images", "Pred_AgeVariant.png"),
       height = 5,  width = 6, dpi = 320)
```
Custom plot

```{r amphkpie_02_54, echo=T, eval = T, message=FALSE, warning=FALSE}
p_emo_var <- plot_model(mf.glmer, type = "pred", terms = c("Emotionality", "Variant"))
#p_emo_var
```

Publishable plot

```{r amphkpie_02_55, echo=T, eval = T, message=FALSE, warning=FALSE}
ggplot(pphi, aes(Emotionality, Probability)) +
  facet_grid(cols = vars(Variant)) +
  stat_summary(fun.y = mean, geom = "point", size = 1.5, color = "gray20") +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", 
               width = 0.2, size = .5, color = "gray20") +
  coord_cartesian(ylim = c(-.1, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10, angle = 90)) +
  labs(x = "Emotionality", y = "Predicted probability") 
ggsave(here::here("images", "Pred_EmoVariant.png"),
       height = 5,  width = 6, dpi = 320)
```

Custom plot

```{r amphkpie_02_56, echo=T, eval = T, message=FALSE, warning=FALSE}
p_grad_var <- plot_model(mf.glmer, type = "pred", terms = c("Gradability", "Variant"))
#p_grad_var
```

Publishable plot

```{r amphkpie_02_57, echo=T, eval = T, message=FALSE, warning=FALSE}
# add prediction
pphi$Prediction <- predict(mf.glmer, pphi, type="response")
# start plotting
ggplot(pphi, aes(Gradability, Prediction, group = Variant, color = Variant, linetype = Variant)) +
  geom_smooth(se = F, method = "lm") +
  coord_cartesian(ylim = c(0, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  labs(x = "Gradability", y = "Predicted probability") +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) 
ggsave(here::here("images", "Pred_GradabilityVariant.png"),
       height = 4,  width = 5, dpi = 320)
```

Custom plot

```{r amphkpie_02_58, echo=T, eval = T, message=FALSE, warning=FALSE}
p_date_gender_var <- plot_model(mf.glmer, type = "pred", terms = c("Date", "Gender", "Variant"))
#p_date_gender_var
```

Publishable plot

```{r amphkpie_02_59, echo=T, eval = T, message=FALSE, warning=FALSE}
ggplot(pphi, aes(Date, Probability, group = Gender, color = Gender)) +
  facet_grid(cols = vars(Variant)) +
  stat_summary(fun.y = mean, geom = "point", size = 1.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", 
               width = 0.2, size = .5) +
  coord_cartesian(ylim = c(-.1, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10, angle = 90)) +
  scale_color_manual(breaks = c("female", "male"),
                     values = c("gray60", "gray20")) +
  labs(x = "Date", y = "Predicted probability")
ggsave(here::here("images", "Pred_DateGenderVariant.png"),
       height = 5,  width = 6, dpi = 320)
```

Custom plot

```{r amphkpie_02_61, echo=T, eval = T, message=FALSE, warning=FALSE}
p_date_priming_var <- plot_model(mf.glmer, type = "pred", terms = c("Date", "Priming", "Variant"))
#p_date_priming_var
```

Publishable plot

```{r amphkpie_02_63, echo=T, eval = T, message=FALSE, warning=FALSE}
ggplot(pphi, aes(Date, Probability, group = Priming, color = Priming)) +
  facet_grid(cols = vars(Variant)) +
  stat_summary(fun.y = mean, geom = "point", size = 1.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", 
               width = 0.2, size = .5) +
  coord_cartesian(ylim = c(-.1, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10, angle = 90)) +
  scale_color_manual(breaks = c("NotPrimed", "Primed"),
                     values = c("gray60", "gray20")) +
  labs(x = "Date", y = "Predicted probability")
ggsave(here::here("images", "Pred_DatePrimingVariant.png"),
       height = 5,  width = 6, dpi = 320)
```

Custom plot

Custom plot

```{r amphkpie_02_71, echo=T, eval = T, message=FALSE, warning=FALSE}
p_gender_priming_var <- plot_model(mf.glmer, type = "pred", terms = c("Priming", "Gender", "Variant"))
#p_gender_priming_var
```

Publishable plot

```{r amphkpie_02_73, echo=T, eval = T, message=FALSE, warning=FALSE}
ggplot(pphi, aes(Priming, Probability, group = Gender, color = Gender)) +
  facet_grid(cols = vars(Variant)) +
  stat_summary(fun.y = mean, geom = "point", size = 1.5) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", 
               width = 0.2, size = .5) +
  coord_cartesian(ylim = c(-.1, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10, angle = 90)) +
  scale_color_manual(breaks = c("female", "male"),
                     values = c("gray60", "gray20")) +
  labs(x = "Date", y = "Predicted probability")
ggsave(here::here("images", "Pred_PrimingGenderVariant.png"),
       height = 5,  width = 6, dpi = 320)
```

Custom plot

```{r amphkpie_02_75, echo=T, eval = T, message=FALSE, warning=FALSE}
p_age_function_var <- plot_model(mf.glmer, type = "pred", terms = c("Age", "Function", "Variant"))
#p_age_function_var
```

Publishable plot

```{r amphkpie_02_77, echo=T, eval = T, message=FALSE, warning=FALSE}
# start plotting
ggplot(pphi, aes(Age, Prediction, group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Function)) +
  geom_smooth(se = F, method = "lm") +
  coord_cartesian(ylim = c(-0.1, 1)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  labs(x = "Age", y = "Predicted probability") +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) + 
  scale_x_discrete(limits = rev(levels(pphi$Age))) 
ggsave(here::here("images", "Pred_AgeFunctionVariant.png"),
       height = 5,  width = 6, dpi = 320)
```
### Visualize random effects

```{r amphkpie_02_79, echo=T, eval = T, message=FALSE, warning=FALSE}
randomtb <- ranef(mf.glmer)$Adjective
rndmlngtb <- data.frame(rownames(randomtb), randomtb)
colnames(rndmlngtb) <- c("Adjective", "Intercept")
rndmlngtb <- rndmlngtb[order(rndmlngtb$Intercept, decreasing = T),]
rndmlngtb
```

```{r amphkpie_02_81, echo=T, eval = T, message=FALSE, warning=FALSE}
summary(rndmlngtb$Intercept)
```
Publishable plot

```{r amphkpie_02_83, echo=T, eval = T, message=FALSE, warning=FALSE}
ggplot(rndmlngtb, aes(Adjective, Intercept)) +
  geom_point(aes(reorder(Adjective, -Intercept, fun = Intercept), y=Intercept)) +
  coord_cartesian(ylim = c(-1, 2)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="none",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10, angle=90)) +
  labs(x = "Adjective type", y = "Adjustment to Intercept")
ggsave(here::here("images", "Pred_Adjectives.png"),
       height = 4,  width = 5, dpi = 320)
```

## Power analysis{-}

```{r amphkpie_02_85, echo=T, eval = T, message=FALSE, warning=FALSE}
# load package
library(simr)
# rename model
gm1 <- mf.glmer
# set seed for replicability
#set.seed(2020011401)
# calculate power for ConversationType
#powerSim(gm1, fixed("ConversationType", "lr"), nsim=100)
```

Extract fixed effecst estimates

```{r amphkpie_02_87, echo=T, eval = T, message=FALSE, warning=FALSE}
estimatesfixedeffects <- fixef(mf.glmer)
exp(estimatesfixedeffects)
```

Change effect size of Variant[really] to make it "medium" (odds ratio = 3.47 or Cohen's d of .5, estimate = 1.245)

```{r amphkpie_02_89, echo=T, eval = T, message=FALSE, warning=FALSE}
fixef(gm1)["Variantreally"] <- 0.519
estimatesfixedeffects <- fixef(gm1)
exp(estimatesfixedeffects)
```

Percent accuracy of the model to detect a medium effect with a likelihood higher than 80 percent.

```{r amphkpie_02_91, echo=T, eval = T, message=FALSE, warning=FALSE}
# set seed for replicability
set.seed(2020011405)
powerSim(gm1, fixed("Variantreally", "z"), nsim=100)
```

Extract session information

```{r amphkpie_02_93, echo=T, eval = T, message=FALSE, warning=FALSE}
sessionInfo()
``` 

=========================THE END=========================