---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English - Part 4"
author: Martin Schweinberger
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: word_document
---

# Introduction{-}

This document shows an analysis of adjective amplification in Hong Kong, Indian, and Philippine English based on the respective components of the International Corpus of English (ICE). 

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

## Preparation{-}

In a first step, the session is prepared by clearing the work space, setting options, activating packages and functions, as well as loading relevant functions.

```{r amphkpie_02_01, echo=T, eval = T, message=TRUE, warning=TRUE}
# clean current workspace
rm(list=ls(all=T))                                      
# load packages
library(tidyverse)
library(dplyr)
library(tidyr)
library(ggplot2)
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)
# define image directory
imageDirectory <- "images"   
```

## Load data{-}

```{r amphkpie_02_03, echo=T, eval = T, message=TRUE, warning=TRUE}
ice <- base::readRDS(file = here::here("data/editdata", "iceamp_04_clean.rda"))
# inspect
head(ice)
```

## Clean data

Factorize predictors and scale frequency

```{r amphkpie_02_05, echo=T, eval = T, message=TRUE, warning=TRUE}
ice <- ice %>%
  select(-Id, -Correction, -SpeechUnit, -SpeechUnitCount, -PreContext, -Token, -L1, 
         -PostContext, -PreContextLong, -Amplified, -Nationality, -OtherLanguages, -Birthplace) %>%
  dplyr::mutate(Emotionality = ifelse(Emotionality == "PositiveEmotional", "Positive",
                               ifelse(Emotionality == "NonEmotional", "Neutral", "Negative")),
                Emotionality = factor(Emotionality, levels = c("Negative", "Neutral", "Positive")),
                Frequency = as.vector(scale(Frequency)),
                Gender = factor(Gender),
                EducationLevel = factor(EducationLevel),
                Priming = factor(Priming),
                Emotionality = factor(Emotionality),
                Function = factor(Function),
                Ethnicity = factor(Ethnicity),
                SemanticCategory = factor(SemanticCategory),
                Speaker = paste0(File, "$", Speaker)) %>%
  select(-File, -WordCount)
str(ice)
```

Determine adjective frequency

```{r amphkpie_02_07, echo=T, eval = T, message=TRUE, warning=TRUE}
fadj <- names(table(ice$Adjective))[which(table(ice$Adjective) > 50)]
fadj
```

Determine variant frequency

```{r amphkpie_02_09, echo=T, eval = T, message=TRUE, warning=TRUE}
famp <- names(table(ice$Variant))[which(table(ice$Variant) > 50)]
famp
```
Collapse infrequent adjectives and amplifiers

```{r amphkpie_02_11, echo=T, eval = T, message=TRUE, warning=TRUE}
ice <- ice %>%
  mutate(Adjective = ifelse(Adjective %in% fadj, Adjective, "other"),
         Variant = ifelse(Variant %in% famp, Variant, "other"),
         Adjective = factor(Adjective),
         Variant = factor(Variant)) %>%
  group_by(Corpus) %>%
  mutate(Frequency = scale(Frequency)[,1])
str(ice)
```

## Data inspection{-}

### Tables

```{r}
# process
tb1a <- ice %>%
  group_by(Corpus, Age, Gender) %>%
  summarize(Adjectives = n(),
            VariantType = names(table(Variant)),
            VariantsN = table(Variant),
            VariantsP = round(VariantsN/Adjectives*100, 1),
            Percent = paste0(VariantsP, "% (N=", VariantsN, ")")) %>%
  select(-VariantsN, -VariantsP) %>%
  tidyr::spread(VariantType, Percent) %>%
  ungroup()
# inspect data
tb1a
```

```{r}
tb1b <- ice %>%
  group_by(Corpus) %>%
  summarize(Adjectives = n(),
            VariantType = names(table(Variant)),
            VariantsN = table(Variant),
            VariantsP = round(VariantsN/Adjectives*100, 1),
            Percent = paste0(VariantsP, "% (N=", VariantsN, ")")) %>%
  select(-VariantsN, -VariantsP) %>%
  tidyr::spread(VariantType, Percent) %>%
  ungroup() %>%
  mutate(Age = "Total",
         Gender = "Total")
# inspect data
tb1b
```

```{r}
# activate package
library(here)
tb1 <- add_row(tb1a, tb1b) %>%
  arrange(Corpus)
# save table
write.table(tb1, here::here("tables", "tb1.txt"), sep = "\t", row.names = F)
# inspect data
tb1
```

### Viz

Visualize Variant by Corpus and Age

```{r amphkpie_02_13, echo=T, eval = T, message=TRUE, warning=TRUE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) + 
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) 
ggsave(file = here("images", "VariantAgeCorpus.png"),
         height = 4,  width = 6, dpi = 320)
  
```

Visualize Variant by Corpus and Age and Function

```{r amphkpie_02_15, echo=T, eval = T, message=TRUE, warning=TRUE}
ice %>%
  mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", 3, 
               ifelse(Age == "26-40"|Age == "26-41", 2, 
               ifelse(Age == "41+"|Age == "42+", 1, Age))),
         Corpus = ifelse(Corpus == "ICE-HK", "ICE Hong Kong",
                  ifelse(Corpus == "ICE-IND", "ICE India", "ICE Philippines"))) %>%
  group_by(Corpus, Age, Variant, Function) %>%
  summarise(Frequency = n()) %>%
  group_by(Corpus, Age, Function) %>%
  mutate(AllSlots = sum(Frequency),
         Percent = round(Frequency/AllSlots*100, 1)) %>%
  select(-Frequency, -AllSlots) %>%
  ggplot(aes(x = Age, y = Percent, 
             group = Variant, color = Variant, linetype = Variant)) +
  facet_grid(cols = vars(Corpus), rows=vars(Function)) +
  geom_line() + 
  coord_cartesian(ylim = c(0, 100)) +
  theme_set(theme_bw(base_size = 12)) +
  theme(legend.position="top", 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.text.x = element_text(size=10)) +
  scale_color_manual(breaks = c("other", "really", "so", "very"),
                     values = c("gray80", "gray60", "gray40", "gray20")) +
  scale_linetype_manual(breaks = c("other", "really", "so", "very"),
                        values = c(4, 3, 2, 1)) +  
  scale_x_discrete(breaks = 1:3, 
                   labels = c("41+", "26-41", "16-25")) 
ggsave(file = here("images", "VariantAgeCorpusFunction.png"),
         height = 4,  width = 6, dpi = 320)
  
```

```{r amphkpie_02_17, echo=T, eval = T, message=TRUE, warning=TRUE}
ice <- ice %>%
  ungroup() %>%
  select(-Speaker) %>%
    mutate(Age = ifelse(Age == "16-25"|Age == "17-25"|Age == "18-25", "16-25", 
               ifelse(Age == "26-40"|Age == "26-41", "26-41", 
               ifelse(Age == "41+"|Age == "42+", "42+", Age)))) %>%
  mutate(Date = ifelse(Date == "1991"|Date == "1992", "Before1993", "After1998"),
         Date = factor(Date, levels = c("Before1993", "After1998")),
         Age = factor(Age),
         Corpus = factor(Corpus),
         SemanticCategory = ifelse(SemanticCategory == "Value", "Value", "Other"),
         SemanticCategory = factor(SemanticCategory),
         Adjective = ifelse(Adjective == "different", "different", "other"),
         Adjective = factor(Adjective)) %>%
  select(-EducationLevel) %>%
  droplevels()
# inspect
head(ice)
```

# Conditional Inference Tree Analysis{-}

```{r amphkpie_02_15, echo=T, eval = T, message=TRUE, warning=TRUE}
library(partykit)
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# apply bonferroni correction (1 minus alpha multiplied by n of predictors)
control = ctree_control(mincriterion = 1-(.05*(ncol(ice)-1)))
# create initial conditional inference tree model
citd.ctree <- ctree(Variant ~ Corpus + Adjective + Age + Gender + Function + Date + Emotionality + SemanticCategory +  Gradability, data = ice)
# save plot
png(here("images", "cit.png"),  width = 4800, height = 1000) 
plot(citd.ctree, gp = gpar(fontsize = 18))
dev.off()
# show plot
plot(citd.ctree, gp = gpar(fontsize = 8))
```


```{r}
# activate package
library(ggparty)
# plotting
ggparty(citd.ctree) +
  geom_edge() +
  geom_edge_label(size = 1.5) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste("N = ", nodesize), 
                                       size = 5)),
                  line_gpar = list(list(size = 5), list(size = 5)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("Node ", id, ", N = ", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.0, 
                  nudge_x = 0.01, 
                  size = 1.5) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_dodge()),
      theme_minimal(base_size = 5),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 700, 100),
                         limits = c(0, 700)),
      xlab(""), 
      ylab("Frequency of Variants")),
    shared_axis_labels = TRUE)
ggsave(file = here("images", "CIT_combined.png"),
         height = 5,  width = 10, dpi = 320)
```


## ggparty

```{r}
# extract p-values
pvals <- unlist(nodeapply(citd.ctree, ids = nodeids(citd.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
ggparty(citd.ctree) +
  geom_edge() +
  geom_edge_label(size = 1.75) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 7)),
                  line_gpar = list(list(size = 7), list(size = 7)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("Node ", id, ", N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 1.75) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 7),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
      shared_axis_labels = TRUE)
ggsave(file = here("images", "CIT_combined_fill.png"),
         height = 5,  width = 10, dpi = 320)
```

## ICE-PHI{-}

```{r amphkpie_02_15, echo=T, eval = T, message=TRUE, warning=TRUE}
phi <- ice %>%
  filter(Corpus == "ICE-PHI") %>%
  select(-Corpus)
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# apply bonferroni correction (1 minus alpha multiplied by n of predictors)
control = ctree_control(mincriterion = 1-(.05*(ncol(phi)-1)))
# create initial conditional inference tree model
citd.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function + Date + Emotionality + SemanticCategory +  Gradability, data = phi)
# save plot
png(here("images", "citphi.png"),  width = 1800, height = 480) 
plot(citd.ctree, gp = gpar(fontsize = 18))
dev.off()
# show plot
plot(citd.ctree, gp = gpar(fontsize = 8))
```


## ggparty

```{r}
# extract p-values
pvals <- unlist(nodeapply(citd.ctree, ids = nodeids(citd.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
ggparty(citd.ctree) +
  geom_edge() +
  geom_edge_label(size = 3) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 12)),
                  line_gpar = list(list(size = 12), list(size = 12)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("Node ", id, ", N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 3) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 12),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
    shared_axis_labels = TRUE)
ggsave(file = here("images", "CIT_PHI.png"),
         height = 5,  width = 10, dpi = 320)
```

## ICE-IND{-}

```{r amphkpie_02_15, echo=T, eval = T, message=TRUE, warning=TRUE}
ind <- ice %>%
  filter(Corpus == "ICE-IND") %>%
  select(-Corpus)
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# apply bonferroni correction (1 minus alpha multiplied by n of predictors)
control = ctree_control(mincriterion = 1-(.05*(ncol(phi)-1)))
# create initial conditional inference tree model
citd.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function + Date + Emotionality + SemanticCategory +  Gradability, data = ind)
# save plot
png(here("images", "citind.png"),  width = 1800, height = 480) 
plot(citd.ctree, gp = gpar(fontsize = 18))
dev.off()
# show plot
plot(citd.ctree, gp = gpar(fontsize = 8))
```


## ggparty

```{r}
# extract p-values
pvals <- unlist(nodeapply(citd.ctree, ids = nodeids(citd.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
ggparty(citd.ctree) +
  geom_edge() +
  geom_edge_label(size = 3) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 12)),
                  line_gpar = list(list(size = 12), list(size = 12)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("Node ", id, ", N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 3) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 12),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
    shared_axis_labels = TRUE) +
  ggsave(file = here("images", "CIT_IND.png"),
         height = 5,  width = 10, dpi = 320)
```


## ICE-HK{-}

```{r amphkpie_02_15, echo=T, eval = T, message=TRUE, warning=TRUE}
hk <- ice %>%
  filter(Corpus == "ICE-HK") %>%
  select(-Corpus)
# set.seed (to store random numbers and thus make results reproducible)
set.seed(2020083001) 
# apply bonferroni correction (1 minus alpha multiplied by n of predictors)
control = ctree_control(mincriterion = 1-(.05*(ncol(phi)-1)))
# create initial conditional inference tree model
citd.ctree <- ctree(Variant ~ Adjective + Age + Gender + Function + Date + Emotionality + SemanticCategory +  Gradability, data = hk)
# save plot
png(here("images", "cithk.png"),  width = 1800, height = 480) 
plot(citd.ctree, gp = gpar(fontsize = 18))
dev.off()
# show plot
plot(citd.ctree, gp = gpar(fontsize = 8))
```

## ggparty

```{r}
# plotting
# extract p-values
pvals <- unlist(nodeapply(citd.ctree, ids = nodeids(citd.ctree), function(n) info_node(n)$p.value))
pvals <- pvals[pvals <.05]
# plotting
ggparty(citd.ctree) +
  geom_edge() +
  geom_edge_label(size = 3) +
  geom_node_label(line_list = list(aes(label = splitvar),
                                   aes(label = paste0("N=", nodesize, ", p", ifelse(pvals < .001, "<.001", paste0("=", round(pvals, 3)))), 
                                       size = 12)),
                  line_gpar = list(list(size = 12), list(size = 12)), 
                  ids = "inner") +
  geom_node_label(aes(label = paste0("Node ", id, ", N=", nodesize)),
                  ids = "terminal", 
                  nudge_y = 0.01, 
                  nudge_x = 0.01, 
                  size = 3) +
  geom_node_plot(gglist = list(geom_bar(aes(x = "", fill = Variant),
                                        position = position_fill()),
      theme_minimal(base_size = 12),
      theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank()),
      scale_fill_manual(values = c("gray20", "gray40", "gray60", "gray80")),
      scale_y_continuous(breaks = seq(0, 1, .2)),
      xlab(""), 
      ylab("Probability")),
    shared_axis_labels = TRUE)
ggsave(file = here("images", "CIT_HK.png"),
         height = 5,  width = 10, dpi = 320)
```

# Outro

```{r}
sessionInfo()
```

***

THE END

***

