---
title: "A corpus-based analysis of ongoing change in the adjective amplifier systems of Hong Kong, Philippine, and Indian English"
author: Martin Schweinberger
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  word_document:
    fig_caption: yes
    pandoc_args: --smart
bibliography: D:\\BibTex/Bibliography.bib
---

# Introduction{-}

This document shows an analysis of adjective amplification in Irish English based on the Irish component of the International Corpus of English (ICE).  

# Preparation{-}

In a first step, the session is prepared by clearing the work space, setting options, activating packages and functions, as well as loading relevant functions.

```{r amphkpie_01_01, echo=T, eval = T, message=FALSE, warning=FALSE}
# load packages
library(tidyverse)  
library(quanteda)
library(syuzhet)
library(NLP)
library(openNLP)
library(qdap)
library(here)
# load function (for pos-tagging objects in R)
source("D:\\R/POStagObject.R")
# set options
options(stringsAsFactors = F)                           
options(scipen = 999) 
options(max.print=10000)
# specify path to corpra
hkpath <- "D:\\Uni\\Korpora\\Original\\ICE Hong Kong"
phipath <- "D:\\Uni\\Korpora\\Original\\ICE Philippines\\Corpus"
indpath <- "D:\\Uni\\Korpora\\Original\\ICE India\\Corpus"
biohkpath <- "D:\\Uni\\Korpora\\Metadata/BiodataIceHongKong_new.txt"
biophipath <- "D:\\Uni\\Korpora\\Metadata/BiodataIcePhilippines.txt"
bioindpath <- "D:\\Uni\\Korpora\\Metadata/BiodataIceIndia.txt"
```

# Data Processing{-}

Define files

```{r amphkpie_01_03, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_files <- list.files(hkpath, pattern = "[S|s]1[A|a].*.txt", full.names = T)
icephi_files <- list.files(phipath, pattern = "S1A.*.TXT", full.names = T)
iceind_files <- list.files(indpath, pattern = "[S|s]1[A|a].*.txt", full.names = T)
```

## Load data{-}

HK

```{r amphkpie_01_05, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk <- sapply(icehk_files, function(x){
  x <- scan(x, what = "char", sep = "", quote = "", quiet = T, skipNul = T)
  x <- paste(x, sep = " ", collapse = " ")
  x <- str_squish(x)
})
# inspect
str(icehk)
```

PHI

```{r amphkpie_01_07, echo=T, eval = T, message=FALSE, warning=FALSE}
icephi <- sapply(icephi_files, function(x){
  x <- scan(x, what = "char", sep = "", quote = "", quiet = T, skipNul = T)
  x <- paste(x, sep = " ", collapse = " ")
  x <- str_squish(x)
})
# inspect
str(icephi)
```

IND

```{r amphkpie_01_09, echo=T, eval = T, message=FALSE, warning=FALSE}
iceind <- sapply(iceind_files, function(x){
  x <- scan(x, what = "char", sep = "", quote = "", quiet = T, skipNul = T)
  x <- paste(x, sep = " ", collapse = " ")
  x <- str_squish(x)
})
# inspect
str(iceind)
```

## Tabulate data{-}

HK

```{r amphkpie_01_11, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_df <- unlist(stringr::str_split(stringr::str_replace_all(icehk,
                                                               "<ICE-HK:[S|s]1[A|a]-",
                                                               "~~~<ICE-HK:S1A-"),
                                      "~~~"))
# create df 
icehk_df <- tibble(1:length(icehk_df),
                  rep("ICE-HK", length(icehk_df)),
                  str_remove_all(icehk_df, "#.*"),
                  str_remove_all(icehk_df, ">.*"), 
                  icehk_df)
# add column names
icehk_df <- icehk_df %>%
  rename(Id = colnames(icehk_df)[1],
         Corpus = colnames(icehk_df)[2],
         File = colnames(icehk_df)[3],
         Speaker = colnames(icehk_df)[4],
         SpeechUnit = colnames(icehk_df)[5]) %>%
  mutate(File = str_remove_all(File, ".*:"),
         Speaker = str_remove_all(Speaker, ".*#"),
         ExtraCorpusSpeaker = ifelse(str_detect(Speaker, "^X") == T, 1, 0),
         Speaker = str_remove_all(Speaker, ".*:"),
         SpeechUnit = str_remove(SpeechUnit, ".*? "),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<[:alnum:]{1,}>.*?</[:alnum:]{1,}>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "<&>.*?</&>"),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<.*?>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "[^[:alnum:]=\\'\\.\\-\\? ]"),
         CleanSpeechUnit = str_squish(CleanSpeechUnit)) %>%
  filter(ExtraCorpusSpeaker == 0,
         CleanSpeechUnit != "",
         Speaker  != "") %>%
  select(-ExtraCorpusSpeaker)
# inspect
str(icehk_df)
```

Extract speech units and word counts: HK

```{r amphkpie_01_13, echo=T, eval = T, message=FALSE, warning=FALSE}
WordCount_HK <- icehk_df %>%
  mutate(WordCount = str_count(CleanSpeechUnit, " ") +1) %>%
  group_by(File, Speaker) %>%
  summarise(SpeechUnitCount = n(),
            WordCount = sum(WordCount))
# inspect
head(WordCount_HK)
```

PHI

```{r amphkpie_01_15, echo=T, eval = T, message=FALSE, warning=FALSE}
icephi_df <- unlist(stringr::str_split(stringr::str_replace_all(icephi, "<ICE-PHI:[S|s]1[A|a]-",
                                                                "~~~<ICE-PHI:S1A-"), "~~~"))
# create df 
icephi_df <- tibble(1:length(icephi_df),
                  rep("ICE-PHI", length(icephi_df)),
                  str_remove_all(icephi_df, "#.*"),
                  str_remove_all(icephi_df, ">.*"), 
                  icephi_df)
# add column names
icephi_df <- icephi_df %>%
  rename(Id = colnames(icephi_df)[1],
         Corpus = colnames(icephi_df)[2],
         File = colnames(icephi_df)[3],
         Speaker = colnames(icephi_df)[4],
         SpeechUnit = colnames(icephi_df)[5]) %>%
  mutate(File = str_remove_all(File, ".*:"),
         Speaker = str_remove_all(Speaker, ".*#"),
         ExtraCorpusSpeaker = ifelse(str_detect(Speaker, "^X") == T, 1, 0),
         Speaker = str_remove_all(Speaker, ".*:"),
         SpeechUnit = str_remove(SpeechUnit, ".*? "),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<[:alnum:]{1,}>.*?</[:alnum:]{1,}>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "<&>.*?</&>"),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<.*?>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "[^[:alnum:]=\\'\\.\\-\\? ]"),
         CleanSpeechUnit = str_squish(CleanSpeechUnit)) %>%
  filter(ExtraCorpusSpeaker == 0,
         CleanSpeechUnit != "") %>%
  select(-ExtraCorpusSpeaker)
# inspect
str(icephi_df)
```

IND

```{r amphkpie_01_17, echo=T, eval = T, message=FALSE, warning=FALSE}
iceind_df <- unlist(stringr::str_split(stringr::str_replace_all(iceind, "<ICE-IND:[S|s]1[A|a]-",
                                                                "~~~<ICE-IND:S1A-"), "~~~"))
# create df 
iceind_df <- tibble(1:length(iceind_df),
                  rep("ICE-IND", length(iceind_df)),
                  str_remove_all(iceind_df, "#.*"),
                  str_remove_all(iceind_df, ">.*"), 
                  iceind_df)
# add column names
iceind_df <- iceind_df %>%
  rename(Id = colnames(iceind_df)[1],
         Corpus = colnames(iceind_df)[2],
         File = colnames(iceind_df)[3],
         Speaker = colnames(iceind_df)[4],
         SpeechUnit = colnames(iceind_df)[5]) %>%
  mutate(File = str_remove_all(File, ".*:"),
         Speaker = str_remove_all(Speaker, ".*#"),
         ExtraCorpusSpeaker = ifelse(str_detect(Speaker, "^X") == T, 1, 0),
         Speaker = str_remove_all(Speaker, ".*:"),
         SpeechUnit = str_remove(SpeechUnit, ".*? "),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<[:alnum:]{1,}>.*?</[:alnum:]{1,}>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "<&>.*?</&>"),
         CleanSpeechUnit = str_remove_all(SpeechUnit, "<.*?>"),
         CleanSpeechUnit = str_remove_all(CleanSpeechUnit, "[^[:alnum:]=\\'\\.\\-\\? ]"),
         CleanSpeechUnit = str_squish(CleanSpeechUnit)) %>%
  filter(ExtraCorpusSpeaker == 0,
         CleanSpeechUnit != "") %>%
  select(-ExtraCorpusSpeaker)
# inspect
str(iceind_df)
```

## Load biodata{-}

```{r amphkpie_01_19, echo=T, eval = T, message=FALSE, warning=FALSE}
biohk <- read.delim(biohkpath, sep = "\t", header = T, quote = "\"", comment.char = "") %>%
  rename(File = Textcode,
         Speaker = Speaker.ID)
biophi <- read.delim(biophipath, sep = "\t", header = T, quote = "\"", comment.char = "") %>%
  rename(File = text.id,
         Speaker = spk.ref)
bioind <- read.delim(bioindpath, sep = "\t", header = T, quote = "\"", comment.char = "") %>%
  rename(File = text.id,
         Speaker = spk.ref)
#inspect
colnames(biohk); colnames(biophi); colnames(bioind)
```

## Join data and biodata{-}

```{r amphkpie_01_21, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_info <- left_join(icehk_df, WordCount_HK, by = c("File", "Speaker"))
icehk_info <- left_join(icehk_info, biohk, by = c("File", "Speaker"))
icephi_info <- left_join(icephi_df, biophi, by = c("File", "Speaker"))
iceind_info <- left_join(iceind_df, bioind, by = c("File", "Speaker"))
```

Remove superfluous columns

```{r amphkpie_01_23, echo=T, eval = T, message=FALSE, warning=FALSE}
icehk_info <- icehk_info %>%
  select(-Old.File, -Text.Category, -Subtext, -Description.of.Contents, -Last.Name,
         -First.Name, -Chinese.Name, -Primary.Education, -Secondary.Education, 
         -Tertiary.Education, -Professional.Training, -Overseas.Experience, -Affiliations, 
         -Employer, -Recording.Place) %>%
  rename(Date = Recording.Date,
         Ethnicity = Ethnic.Group,
         L1 = Mother.Tongue,
         OtherLanguages = Other.Languages,
         EducationLevel = Educational.Level) %>%
  mutate(Date = str_remove_all(Date, ".*-"),
         Gender = ifelse(Gender == "f", "female", 
                  ifelse(Gender == "m", "male", Gender)))
icephi_info <- icephi_info %>%
  select(-id, -orig.id, -file.speaker.id, -subfile.id, -your.id, -text.category,
         -organizing.body, -first.name, -last.name, -copyright.statement, -recording.place) %>%
  rename(Date = recording.date,
         Gender = gender,
         Age = age,
         Nationality = nationality,
         L1 = mother.tongue,
         Occupation = occupation,
         EducationLevel = educational.level,
         SpeechUnitCount = speech.unit.count,
         WordCount = word.count) %>%
  mutate(Date = str_remove_all(Date, ".*-"),
         Date = str_remove_all(Date, "[:alpha:]"),
         Date = str_squish(Date))
iceind_info <- iceind_info %>%
  select(-id, -file.speaker.id, -subfile.id, -place.of.recording, -text.category, -file.wordcount,
         -communicative.situation, -organising.body, -copyright.statement, -communicative.role,
         -surname, -forenames, -affiliations, -free.comments, -birthplace, -audience.size,
         -no.of.participants, -relationship.of.participants) %>%
  rename(Date = date.of.recording,
         Age = age,
         Gender = gender,
         Nationality = nationality,
         EducationLevel = education,
         Occupation = occupation,
         L1 = mother.tongue,
         OtherLanguages = other.languages,
         SpeechUnitCount = speech.unit.count,
         WordCount = word.count)
# inspect
head(icehk_info, 3)
```

## Create single table{-}
 
```{r amphkpie_01_25, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- merge(icehk_info, icephi_info, all = TRUE)
ice <- merge(ice, iceind_info, all = TRUE)
ice <- ice %>%
  arrange(Corpus, File, Id) %>%
  mutate(Date = str_remove_all(Date, ".* "),
         Date = ifelse(nchar(Date) == 2 & str_detect(Date, "^0"), 
                       paste("20", Date, sep = ""),
                ifelse(nchar(Date) == 2 & str_detect(Date, "^9"), 
                       paste("19", Date, sep = ""),
                       Date)),
         Date = str_replace_all(Date, "1993/94", "1993"),
         Age = ifelse(Age == "60 or above", "60+", Age))
# save data
base::saveRDS(ice, file = here::here("data/rawdata", "ice.rda"))
# inspect
head(ice)
```

## Recode bioinfo

### Recode Age

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  filter(Age != "14-16",
         Age != "") %>%
  mutate(Age = ifelse(Corpus == "ICE-HK" & Age == "41-45", "41+",
               ifelse(Corpus == "ICE-HK" & Age == "46-50", "41+",
               ifelse(Corpus == "ICE-HK" & Age == "60+", "41+",
               ifelse(Corpus == "ICE-HK" & Age == "51-55", "41+",       
               ifelse(Corpus == "ICE-HK" & Age == "17-20", "17-25",
               ifelse(Corpus == "ICE-HK" & Age == "21-25", "17-25",
               ifelse(Corpus == "ICE-HK" & Age == "26-30", "26-40",       
               ifelse(Corpus == "ICE-HK" & Age == "31-35", "26-40",       
               ifelse(Corpus == "ICE-HK" & Age == "36-40", "26-40",
               ifelse(Corpus == "ICE-IND" & Age == "26-33", "26-41",
               ifelse(Corpus == "ICE-IND" & Age == "34-41", "26-41",
               ifelse(Corpus == "ICE-IND" & Age == "42-49", "42+",       
               ifelse(Corpus == "ICE-IND" & Age == "50+", "42+",
               ifelse(Corpus == "ICE-PHI" & Age == "16-20", "16-25",
               ifelse(Corpus == "ICE-PHI" & Age == "21-25", "16-25",
               ifelse(Corpus == "ICE-PHI" & Age == "41-45", "41+",       
               ifelse(Corpus == "ICE-PHI" & Age == "46-50", "41+",       
               ifelse(Corpus == "ICE-PHI" & Age == "50+", "41+", 
               ifelse(Corpus == "ICE-PHI" & Age == "26-30", "26-40",       
               ifelse(Corpus == "ICE-PHI" & Age == "31-35", "26-40",
               ifelse(Corpus == "ICE-PHI" & Age == "36-40", "26-40",       
                      Age))))))))))))))))))))))
# inspect
ftable(ice$Age,ice$Corpus)
```
### Recode Nationality

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(Nationality = str_to_title(Nationality),
         Nationality = str_remove_all(Nationality, " .*"),
         Nationality = ifelse(Corpus == "ICE-HK" & Nationality != "Chinese", "Other",
                       ifelse(Corpus == "ICE-PHI" & Nationality != "Filipino", "Other",
                              Nationality)))
# inspect
ftable(ice$Nationality,ice$Corpus)
```
### Recode L1

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(L1 = str_to_title(L1),
         L1 = str_remove_all(L1, " .*"),
         L1 = str_remove_all(L1, "/.*"),
         L1 = ifelse(Corpus == "ICE-HK" & L1 != "Cantonese", "Other", 
              ifelse(Corpus == "ICE-PHI" & L1 != "Tagalog", "Other",
              ifelse(Corpus == "ICE-IND" & L1 != "Marathi", "Other", L1))))
# inspect
ftable(ice$L1,ice$Corpus)
```

### Remove Occupation (all ACMP!)

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
head(ice)
ice <- ice %>%
  select(-Occupation)
```

### Recode EducationLevel

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
#head(ice)
ice <- ice %>%
  mutate(EducationLevel = tolower(EducationLevel),
         EducationLevel = ifelse(str_detect(EducationLevel, "uni"), "College",
                          ifelse(str_detect(EducationLevel, "college"), "College", 
                                 EducationLevel)),
         EducationLevel = ifelse(Corpus == "ICE-HK" & EducationLevel == "", NA,
                          ifelse(Corpus == "ICE-HK" & EducationLevel != "College",
                                 "NoCollege", 
                          ifelse(Corpus == "ICE-IND" & EducationLevel != "College",
                                 "Other", 
                          ifelse(Corpus == "ICE-PHI" & is.na(EducationLevel) == F,
                                 "College", EducationLevel)))))
# inspect
ftable(ice$EducationLevel,ice$Corpus)
```
### Recode OtherLanguages

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(OtherLanguages = str_to_title(OtherLanguages),
         OtherLanguages = str_remove_all(OtherLanguages, ", .*"),
         OtherLanguages = ifelse(Corpus == "ICE-HK" & OtherLanguages != "English",
                                 "Other",
                          ifelse(Corpus == "ICE-IND" & OtherLanguages != "Hindi",
                                 "Other", OtherLanguages)))
# inspect
ftable(ice$OtherLanguages,ice$Corpus)
```

### Recode Birthplace

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(Birthplace = str_to_title(Birthplace),
         Birthplace = ifelse(Corpus == "ICE-HK" & Birthplace != "Hong Kong",
                                 "Other", Birthplace))
# inspect
ftable(ice$Birthplace,ice$Corpus)
```

### Recode Ethnicity

```{r amphkpie_02_01, echo=T, eval = T, message=FALSE, warning=FALSE}
ice <- ice %>%
  mutate(Ethnicity = str_to_title(Ethnicity),
         Ethnicity = ifelse(Corpus == "ICE-HK" & Ethnicity != "Chinese",
                                 "Other", Ethnicity))
# inspect
ftable(ice$Ethnicity,ice$Corpus)
```

## PoS tagging{-}

```{r amphkpie_01_27, echo=T, eval = T, message=FALSE, warning=FALSE}
# pos tagging data
icepos <- POStag(object = ice$CleanSpeechUnit)
icepos <- as.vector(unlist(icepos))
writeLines(icepos, con = here::here("data/editdata", "icepos.txt"), sep = "\n", useBytes = FALSE)
ice$Tagged <- scan(here::here("data/editdata", "icepos.txt"), what = "char", sep = "\n", quote = "", quiet = T, skipNul = T)
# inspect
head(ice)
```

# Concordancing{-} 

```{r amphkpie_01_29, echo=T, eval = T, message=FALSE, warning=FALSE}
concjj <- as.data.frame(kwic(ice$Tagged, 
                             pattern = 
                               phrase("[:alnum:]{1,} / JJ[:alnum:]{0,}\\${0,1}"),
                             valuetype = "regex",
                             window = 15,
                             case_insensitive = F,
                             preserve_tags = TRUE
                             ))
# clean concjj
concjj <- concjj %>%
  mutate(pre = str_replace_all(pre, " / ", "/"),
         keyword = str_replace_all(keyword, " / ", "/"),
         post = str_replace_all(post, " / ", "/")) %>%
  mutate(pre = str_replace_all(pre, "/ ", "/"),
         keyword = str_replace_all(keyword, "/ ", "/"),
         post = str_replace_all(post, "/ ", "/")) %>%
  mutate(pre = str_replace_all(pre, " \\$", "$"),
         keyword = str_replace_all(keyword, " \\$", "$"),
         post = str_replace_all(post, " \\$", "$"))
# inspect
head(concjj)
```

Count adjectives in speech units

```{r amphkpie_01_31, echo=T, eval = T, message=FALSE, warning=FALSE}
# not repeated
rp0 <- str_count(ice$Tagged, "[:alnum:]/JJ[:alnum:]{0,}\\${0,}")
# repeated without 0
rp1 <- ifelse(rp0 == 0, 1, rp0)
# repeated with 0
rp2 <- rep(rp0, rp1)
```


```{r amphkpie_01_33, echo=T, eval = T, message=FALSE, warning=FALSE}
iceadj <- ice[rep(seq(nrow(ice)), rp1),]
# add number of adjs
iceadj <- data.frame(iceadj, rp2)
# remove speech units without adj
iceadj <- iceadj %>%
  filter(rp2 != 0)
# combine data sets
iceadj <- data.frame(iceadj, concjj) %>%
  select(-rp2, -docname, -from, -to, -pattern) %>%
  rename(Token = keyword,
         PreContext = pre,
         PostContext = post)
# remove rows without Tokens
iceamp <- iceadj %>% 
  filter(is.na(Token) == F) %>%
  mutate(Adjective = tolower(str_remove_all(Token, "/JJ")),
         Variant = tolower(str_remove_all(str_squish(PreContext), ".* ")),
         Id = 1:length(Variant)) %>%
  mutate(Variant = str_remove_all(Variant, "/.*")) %>%
  select(-CleanSpeechUnit, -Tagged)
# inspect data
head(iceamp)
```


# Annotation and cleaning{-}

```{r amphkpie_01_35, echo=T, eval = T, message=FALSE, warning=FALSE}
iceamp <- iceamp %>%
  mutate(Function = str_squish(PostContext)) %>%
  mutate(Function = tolower(Function)) %>%
  mutate(Function = gsub("/jj[a-z]{0,2} ", "qwertz", Function)) %>%
  mutate(Function = gsub("/rb[a-z]{0,2} ", "qwertz", Function)) %>%
  mutate(Function = gsub(" .*", "", Function)) %>%
  mutate(Function = gsub("qwertz", " ", Function)) %>%
  mutate(Function = gsub(".*/nn.*", "Attributive", Function)) %>%
  mutate(Function = ifelse(Function == "Attributive", "Attributive", "Predicative"))
# inspect data
head(iceamp)
```

## Define amplifiers{-}

```{r amphkpie_01_37, echo=T, eval = T, message=FALSE, warning=FALSE}
amplifiers <- c("absolutely", "actually", "aggressively", 
                "amazingly", "appallingly", "awfully", 
                "badly", "bloody", "certainly", "clearly",
                "dead", "completely", "considerably", 
                "crazy", "decidedly", "definitely",  "distinctly", 
                "dreadfully", "enormously", "entirely", "especially", 
                "exactly", "exceedingly", "exceptionally", 
                "excruciatingly", "extraordinarily", "extremely",
                "fiercely", "firmly", "frightfully", "fucking", 
                "fully", "genuinely", "greatly",
                "grossly", "heavily", "highly", "hopelessly", 
                "horrendously", "hugely",
                "immediately", "immensely", "incredibly", 
                "infinitely", "intensely", "irrevocably",
                "mad", "mega", "mighty", "most", "much", 
                "obviously", "openly", "overwhelmingly", "particularly", 
                "perfectly", "plenty", "positively", 
                "pretty", "profoundly", "purely", "real", "really", 
                "remarkably", "seriously", 
                "shocking",   "significantly", "so", 
                "specially", "specifically", "strikingly",
                "strongly", "substantially", "super", "surely", 
                "terribly", "terrifically", 
                "total", "totally", "traditionally", "true", 
                "truly", "ultra", "utterly", "very",
                "viciously", "wholly", "wicked", "wildly")
```

Clean data

```{r amphkpie_01_39, echo=T, eval = T, message=FALSE, warning=FALSE}
# register
iceamp <- iceamp %>%
# shorten post Context
  mutate(PostContext = substr(PostContext, 1, 
                              ifelse((nchar(PostContext)+25) < 25,
                                     max(nchar(PostContext)), 25))) %>%
  # pre Context
  mutate(PreContext = str_squish(PreContext)) %>%
  mutate(PreContextLong  = substr(iceamp$PreContext,
                                  ifelse(nchar(PreContext)-25 <=0, 1, 
                                                              nchar(PreContext)-25),
                                  nchar(PreContext))) %>%
  mutate(PreContext = str_remove_all(PreContext, ".* "),
         Variant = ifelse(Variant %in% amplifiers, Variant, 0),
         Amplified = ifelse(Variant == 0, 0, 1)) %>%
  group_by(Corpus, Adjective, Age) %>%
  mutate(AdjFrequency = n()) %>%
  ungroup() %>%
  group_by(Corpus, Age) %>%
  mutate(AllAdjs = n()) %>%
  mutate(Frequency = round(AdjFrequency/AllAdjs*100, 2),
         Postag = str_remove_all(Token, ".*/")) %>%
  filter(Postag == "JJ",
         Amplified != 0) %>%
  select(-AllAdjs, -AdjFrequency, -Postag)
# inspect
head(iceamp)
```

## Check adjectives{-}

```{r amphkpie_01_41, echo=T, eval = T, message=FALSE, warning=FALSE}
misspelled <- as.vector(unlist(sapply(iceamp$Adjective, function(x){
  x <- which_misspelled(x, suggest=FALSE)
})))
problematic_items <- names(table(misspelled))
# inspect
head(problematic_items)
```

Remove errors

```{r amphkpie_01_43, echo=T, eval = T, message=FALSE, warning=FALSE}
# define forms that require removal
nonpropadj <- c("afs", "ako", "bagay", "comfor", "danke", "embarassing",
                "eto", "extremeawesome", "faluting", "ganon", "gipit", "gwai",
                "inspite", "kamal", "luc", "mahal", "malambing", "ngh", "poch",
                "sarcastical", "tagal", "tamad", "terrib", "uhm", "uhn", "umesh",
                "yaar")
iceamp <- iceamp %>%
  filter(!Adjective %in% nonpropadj)
# extract adjectives for further inspection
adjectives <- names(table(iceamp$Adjective))
# inspect
head(adjectives)
```
## Correct spelling{-}

```{r amphkpie_01_45, echo=T, eval = T, message=FALSE, warning=FALSE}
iceamp$Correction <- as.vector(unlist(sapply(iceamp$Adjective, function(x){
  x <- which_misspelled(x, suggest=T, n.suggests = 1)
  x <- ifelse(is.null(x) == T, "correct", x[3])
})))
# replace adjective with correction
iceamp <- iceamp %>%
  mutate(Adjective = ifelse(Correction != "correct", Correction, Adjective))
# inspect
head(iceamp)
```

## Code priming{-}

```{r amphkpie_01_47, echo=T, eval = T, message=FALSE, warning=FALSE}
# code priming
prim <- c(rep(0, 1), iceamp$Variant[1:length(iceamp$Variant)-1])
primtb <- cbind(iceamp$Variant, prim)
iceamp$Priming <- as.vector(unlist(apply(primtb, 1, function(x){
  x <- ifelse(x[1] == "0" & x[2] == "0", "NotPrimed",
              ifelse(x[1] == x[2], "Primed", "NotPrimed"))
})))
# inspect data
head(iceamp)
```

## Removal of misfits{-}

```{r amphkpie_01_49, echo=T, eval = T, message=FALSE, warning=FALSE}
nrow(iceamp)
sups <- c(".*most.*", ".*more.*") 
negs <- c(".*not.*", ".*never.*", ".*n't.*")
downtoners <- c(".*sort/.*", ".*kind/.*", ".* bit/.*", ".*somewhat.*",
                ".*fairly.*", ".*rather.*", ".*reasonably.*", 
                ".*slightly.*", ".*comparatively.*", ".*semi.*", 
                ".*relatively.*", ".*little.*", ".*somehow.*", 
                ".*almost.*", ".*partly.*", ".*hardly.*", ".* less.*",
                ".*barely.*", ".* just/.*")
specialforms <- c(".* too.*", ".*quite.*", ".*much.*")
postdowntoners <- c(".*enough.*")
iceamp <- iceamp %>%
  filter(!str_detect(PreContextLong, paste(sups,collapse="|")),
         !str_detect(PreContextLong, paste(negs,collapse="|")),
         !str_detect(PreContextLong, paste(downtoners,collapse="|")),
         !str_detect(PreContextLong, paste(specialforms,collapse="|")),
         !str_detect(PostContext, postdowntoners),
         Variant != "")
# inspect
nrow(iceamp)
```

Now, we save the new data set to the disc.

```{r lamphkpie_01_51, echo=T, eval = T, message=FALSE, warning=FALSE}
# save raw data to disc
base::saveRDS(iceamp, file = here::here("data/editdata", "iceamp_02_woneg.rda"))
```

Inspect the remaining adjectives.

```{r amphkpie_01_53, echo=T, eval = T, message=FALSE, warning=FALSE}
# inspect adjectives
adj <- names(table(iceamp$Adjective))
# save adjectives to disc
base::saveRDS(adj, file = here::here("data/editdata", "adj.rda"))
# inspect adjectives
names(table(adj)) 
```


```{r amphkpie_01_55, echo=T, eval = T, message=FALSE, warning=FALSE}
# define forms that require removal
nonpropadj <- c("yeuky", "yon", "di", "huh", "video", "tut", "due", "rugby",
                "okay", "lust", "ex", "de", "very", "much", "many", "few")
iceamp <- iceamp %>%
  filter(!Adjective %in% nonpropadj)
# save raw data to disc
base::saveRDS(adj, file = here::here("data/editdata", "iceamp_03_semiclean.rda"))
# inspect data
head(iceamp)
```

## Gradability{-}

Gradability scores are derived from BNC

```{r amphkpie_01_57, echo=T, eval = T, message=FALSE, warning=FALSE}
# load gradability scores (derived from BNC)
gradability <- read.delim(here::here("data/supdata", "Gradability_bnc.txt"), sep = "\t", header = T, quote = "", skipNul = T)
iceamp$Gradability <- ifelse(iceamp$Adjective %in% gradability$Adjective, gradability$Beta, 1)
# inspect 
head(iceamp)
```

## Semantic classification{-}

Semantic categories (@tagliamonte2008intensifiers, based on @dixon1977adjectives)

- dimension = semdim (e.g. *big*, *large*, *little*, *small*, *long*, *short*, *wide*, *narrow*, *thick*)

- difficulty = semdif (e.g. *difficult*, *simple*)

- physical property = (e.g. *hard*, *soft*, *heavy*, *light*, *rough*, *smooth*, *hot*, *sweet*)

- color = semcol (e.g. *black*, *white*, *red*)

- human propensity: semhup (e.g. *jealous*, *happy*, *kind*, *clever*, *generous*, *gay*, *rude*)

- age = semage (e.g. *new*, *young*, *old*) 

- value (e.g. *good*, *bad*, *proper*, *perfect*, *excellent*, *delicious*, *poor*)

- speed  (e.g. *fast*, *quick*, *slow*)

- position (e.g. *right*, *left*, *near*, *far*)

- other



```{r amphkpie_01_59, echo=T, eval = T, message=FALSE, warning=FALSE}
# age
semage <- c("actual", "adolescent", "aged", "ancestral", "ancient", 
            "annual", "archaeological", "archaic", "biographical",
            "contemporary", "elderly", "foster", "generational", 
            "historic", "historical", "immature", "junior", "late", 
            "mature", "medieval", "modern", "old", "oldfashioned", 
            "outdated", "past", "preliminary", "present", "primary", 
            "prime", "prior", "puerile", "recent", "seasonal",
            "senile", "senior", "temporary", "topical", "veteran", 
            "young", "youthful")
# color
semcol <- c("colourful", "darkened", "pinkish", "reddish", "black", 
            "blue", "brown", "coloured", "dark", "gold", "golden", 
            "gray", "green", "grey", "lime", "marine", "orange", 
            "pink", "purple", "red", "silver", "white", "yellow")
semdif <- c("basic", "complicated", "difficult", "easy", "elusive", 
            "facile", "precarious", "risky", "simple", "stressful", 
            "tricky", "twisted", "unpromising")
# dimension
semdim <- c("adjacent", "angled", "arctic", "back", "backward", "big", 
            "bottom", "brief", "bright", "broad", "central", "centralised",
            "centred", "close", "compact", "deep", "diagonal", 
            "direct", "distant", "distorted", "down", "downward", 
            "early", "east", "easterly", "eastern", "endemic", "endless",
            "equatorial", "european", "ewen", "far", "few", "first", "flat", 
            "foreign", "foremost", "forthcoming", "forward", "free", 
            "front", "frontal", "further", "geographical", "giant", 
            "gigantic", "global", "grand", "half", "halved", "halving", 
            "high", "horizontal", "huge", "inner", "inside", "internal",
            "international", "large", "last", "latter", "left", "linear",
            "little", "local", "locating", "long", "low", "massive", 
            "micro", "mid", "middle", "minimal", "minimalist", 
            "minimum", "minor", "misleading", "narrow", "national", 
            "nationwide", "native", "near", "nearby", "next", "north",
            "northern", "off", "onward", "orientated", "outside", "over",
            "overhanging", "overlapping", "pacific", "parallel", "paramount",
            "peripheral", "petite", "polar", "proportional", "provincial", 
            "public", "rear", "regional", "remote", "reverse", "round", 
            "rural", "separate", "separated", "short", "sizeable", "slight",
            "small", "south", "southern", "southwest", "spinal", "square",
            "steep", "stratospheric", "suburban", "super", "tall", "teensy", 
            "terminal", "territorial", "thick", "thickened", "thin", 
            "tight", "tiny", "titanic", "top", "torrential", "touring",
            "tremendous", "under", "universal", "unseeded", "upward", 
            "urban", "urbanised", "vast", "vertical", "warped", "wee", 
            "west", "western", "wide", "widespread")
semhup <- c("able", "abrasive", "abusive", "academic", "accomplished",
            "advanced", "adverse", "afraid", "aggressive", "aimless", 
            "amused", "amusing", "analytical", "angry", "anxious",
            "appreciative", "apprehensive", "ashamed", "astute", "aware",
            "benevolent", "besetting", "blind", "bold", "bossy", 
            "brave", "brutal", "busy", "callous", "candid", "capable", 
            "careful", "challenging", "charismatic", "cheated", "clever",
            "cocky", "compelling", "competent", "competitive", 
            "concerned", "confident", "consultative", "convinced", 
            "creative", "cross", "cruel", "cute", 
            "cynical", "delighted", "depressed", "despairing", 
            "desperate", "despondent", "disappointed", 
            "dodgy", "dotty", "dubious", "dull", "dumb", "eager", 
            "elitist", "embarrassed", "emotional", "encouraging", 
            "entertaining", "enthusiastic", "erudite", "evil", "excited",
            "fanatic", "fearful", "ferocious", 
            "fierce", "foolish", "forceful", "fortunate", "fraudulent",
            "friendly", "frustrated", "fun", 
            "funny", "furious", "generous", "gifted", "glad", 
            "goodhearted", "gracious", "grateful", 
            "grim", "gross", "gutless", "hairy", "hapless", "happy",
            "hopeful", "hopeless", "horrible", "hostile", 
            "hysterical", "ignorant", "ill", "imperative", 
            "incompetent", "inexorable", "inexperienced", 
            "infallible", "informed", "insatiable", "insidious", 
            "intellectual", "intelligent", "intriguing", 
            "inventive", "jealous", "joyful", "keen", "lazy", 
            "learned", "learnt", "loath", "lone", "lonely", 
            "lucky", "lunatic", "mad", "mean", "minded", "motivating", 
            "nasty", "nervous", "nice", 
            "optimistic", "passionate", "patronising", "pessimistic", 
            "pleased", "polite", "poor", 
            "preachy", "prepared", "presumptuous", "primitive", 
            "procedural", "professional", "promotional", 
            "proud", "prudential", "psycho", "puzzled", "rapt", 
            "rational", "regretful", "relentless", 
            "resourceful", "respected", "rich", "romantic", "rowdy", 
            "rude", "sad", "sane", "sarcastic", 
            "satisfied", "satisfying", "scared", "sceptical", 
            "selective", "selfish", "sensitive", 
            "sentimental", "sick", "silly", "skilful", "skilled", 
            "smart", "snotty", "sociable", "sophisticated", 
            "sorry", "sovereign", "spiteful", "staunch", "strategic", 
            "strict", "stubborn", "stupid", 
            "suffering", "superior", "supportive", "suspicious", 
            "tactic", "talented", "technical", "treacherous", 
            "troubled", "unable", "unanswered", "unaware", "uncaring",
            "ungrateful", "unhappy", "unsmiling", 
            "unsocial", "upset", "valiant", "valid", "vengeful", 
            "vile", "wicked", "willing", "wise", "witty", "worried")
# physical property
semphy <- c("cheap", "clear", "cold", "comfortable", "cool", "dark", 
            "different", "dry", "flexible", "hard", 
            "heavy", "hot", "light", "neat", "obvious", "quick", 
            "quiet", "real", "same", "scarce", "similar", 
            "slow", "strong", "sweet", "tidy", "warm")
# Value
semval <- c("amazing", "appropriate", "awful", "bad", "beautiful", 
            "bizarre", "boring", "brilliant", 
            "competitive", "counterproductive", "dangerous", "easy", 
            "effective", "efficient", "essential", "excellent", 
            "exciting", "expensive", "fantastic", "fat", "good", 
            "great", "important", "inadequate", "interesting", 
            "new", "original", "painful", "pathetic", "popular", 
            "positive", "relevant", "ridiculous", "right", 
            "scary", "serious", "simple", "special", "strange", 
            "sure", "terrible", "tough", "trendy", "true", "ugly",  
            "uncomfortable", "unrealistic", "unusual", "useful", 
            "useless", "weird", "wealthy", "worser", "worthwhile", 
            "wrong", "yummy")
# add semantic type classification
iceamp <- iceamp %>%
  dplyr::mutate(SemanticCategory = ifelse(Adjective %in% semage, "Age", 
                                   ifelse(Adjective %in% semcol, "Color",
                                   ifelse(Adjective %in% semdif, "Difficulty",
                                   ifelse(Adjective %in% semdim, "Dimension",
                                   ifelse(Adjective %in% semhup,
                                          "HumanPropensity", 
                                  ifelse(Adjective %in% semphy,
                                         "PhysicalProperty", 
                                  ifelse(Adjective %in% semval, "Value",
                                         Adjective)))))))) %>%
  dplyr::mutate(SemanticCategory = ifelse(SemanticCategory == "Age" | SemanticCategory == "Color" | SemanticCategory == "Difficulty" | SemanticCategory == "Dimension" | SemanticCategory == "HumanPropensity" | SemanticCategory == "PhysicalProperty" | SemanticCategory == "Value", SemanticCategory, "Other"))
# extract adjectives and their semantic class
iceamp_adjs <- iceamp %>%
  dplyr::select(Adjective, SemanticCategory) %>%
  unique()
# save raw data to disc
base::saveRDS(adj, file = here::here("data/editdata", "adj_semclass.rda"))
# table sem class of tokens
table(iceamp$SemanticCategory)
```

## Coding emotionality{-}

Sentiment analysis

```{r amphkpie_01_63, echo=T, eval = T, message=FALSE, warning=FALSE}
# code emotion
class_emo <- get_nrc_sentiment(iceamp$Adjective)
# process sentiment
iceamp$Emotionality <- as.vector(unlist(apply(class_emo, 1, function(x){
  x <- ifelse(x[9] == 1, "NegativeEmotional",
              ifelse(x[10] == 1, "PositiveEmotional", "NonEmotional")) } )))
# revert order of factor Emotionality
iceamp$Emotionality <- factor(iceamp$Emotionality, levels = c("NonEmotional", "NegativeEmotional", "PositiveEmotional"))
# inspect data
head(iceamp)
```

# Data testing

Recode so as predicative

```{r amphkpie_01_67, echo=T, eval = T, message=FALSE, warning=FALSE}
iceamp <- iceamp %>%
  mutate(Function = ifelse(Variant == "so", "Predicative", Function))
nrow(iceamp)
```

```{r amphkpie_01_65, echo=T, eval = T, message=FALSE, warning=FALSE}
so_ex <- iceamp %>%
  select(Id, Corpus, File, Variant, SpeechUnit, PreContextLong, Token, PostContext, Function) %>%
  filter(Variant == "so")
# inspect
head(so_ex)
```

Manual correction

```{r amphkpie_01_67, echo=T, eval = T, message=FALSE, warning=FALSE}
iceamp_edited <- iceamp %>%
  mutate(Function = case_when(
      Variant == "so" & Corpus == "ICE-HK" & File == "S1A-022" & Id == "3280" ~ "Attributive",
      Variant == "so" & Corpus == "ICE-HK" & File == "S1A-080" & Id == "12308" ~ "Attributive",
      Variant == "so" & Corpus == "ICE-IND" & File == "S1A-017" & Id == "17694" ~ "Attributive",
      Variant == "so" & Corpus == "ICE-IND" & File == "S1A-022" & Id == "18168" ~ "Attributive",
      Variant == "so" & Corpus == "ICE-IND" & File == "S1A-065" & Id == "22939" ~ "Attributive",
      Variant == "so" & Corpus == "ICE-IND" & File == "S1A-066" & Id == "23060" ~ "Attributive",
      TRUE ~ Function
  )) %>%
  filter(!(Id == "2937" & Corpus == "ICE-HK" & File == "S1A-020")) %>%
  filter(!(Id == "4689" & Corpus == "ICE-HK" & File == "S1A-031")) %>%
  filter(!(Id == "8761" & Corpus == "ICE-HK" & File == "S1A-056")) %>%
  filter(!(Id == "9652" & Corpus == "ICE-HK" & File == "S1A-061")) %>%
  filter(!(Id == "10217" & Corpus == "ICE-HK" & File == "S1A-065")) %>%
  filter(!(Id == "10555" & Corpus == "ICE-HK" & File == "S1A-067")) %>%
  filter(!(Id == "11009" & Corpus == "ICE-HK" & File == "S1A-070")) %>%
  filter(!(Id == "11488" & Corpus == "ICE-HK" & File == "S1A-073")) %>%
  filter(!(Id == "11897" & Corpus == "ICE-HK" & File == "S1A-077")) %>%
  filter(!(Id == "14623" & Corpus == "ICE-HK" & File == "S1A-094")) %>%
  filter(!(Id == "15965" & Corpus == "ICE-IND" & File == "S1A-003")) %>%
  filter(!(Id == "16060" & Corpus == "ICE-IND" & File == "S1A-004")) %>%
  filter(!(Id == "16462" & Corpus == "ICE-IND" & File == "S1A-006")) %>%
  filter(!(Id == "17092" & Corpus == "ICE-IND" & File == "S1A-012")) %>%
  filter(!(Id == "17109" & Corpus == "ICE-IND" & File == "S1A-012")) %>%
  filter(!(Id == "17418" & Corpus == "ICE-IND" & File == "S1A-015")) %>%
  filter(!(Id == "17716" & Corpus == "ICE-IND" & File == "S1A-017")) %>%
  filter(!(Id == "17991" & Corpus == "ICE-IND" & File == "S1A-020")) %>%
  filter(!(Id == "18348" & Corpus == "ICE-IND" & File == "S1A-023")) %>%
  filter(!(Id == "20609" & Corpus == "ICE-IND" & File == "S1A-043")) %>%
  filter(!(Id == "21139" & Corpus == "ICE-IND" & File == "S1A-048")) %>%
  filter(!(Id == "22809" & Corpus == "ICE-IND" & File == "S1A-064")) %>%
  filter(!(Id == "22951" & Corpus == "ICE-IND" & File == "S1A-065")) %>%
  filter(!(Id == "23000" & Corpus == "ICE-IND" & File == "S1A-065")) %>%
  filter(!(Id == "24242" & Corpus == "ICE-IND" & File == "S1A-075")) %>%
  filter(!(Id == "24500" & Corpus == "ICE-IND" & File == "S1A-078")) %>%
  filter(!(Id == "26149" & Corpus == "ICE-IND" & File == "S1A-090")) %>%
  filter(!(Id == "27474" & Corpus == "ICE-PHI" & File == "S1A-004")) %>%
  filter(!(Id == "33382" & Corpus == "ICE-PHI" & File == "S1A-062")) %>%
  filter(!(Id == "34235" & Corpus == "ICE-PHI" & File == "S1A-071")) %>%
  filter(!(Id == "34431" & Corpus == "ICE-PHI" & File == "S1A-073"))
# save raw data to disc
base::saveRDS(iceamp_edited, file = here::here("data/editdata", "iceamp_04_clean.rda"))
# inspect
nrow(iceamp_edited)
nrow(iceamp)
```

## Example extraction{-}

```{r amphkpie_01_61, echo=T, eval = T, message=FALSE, warning=FALSE}
ex <- iceamp_edited %>%
  dplyr::select(File, Function, PreContextLong, Adjective, PostContext, Variant) %>%
  dplyr::mutate(Example = paste(PreContextLong, Adjective, PostContext, sep = " ")) %>%
  dplyr::select(File, Function, Example, Variant) %>%
  dplyr::mutate(Example = str_remove_all(Example, "/[A-Z]{2,}\\${0,1}")) %>%
  dplyr::filter(Variant != "0") %>%
  dplyr::mutate(Id = 1:length(Example)) %>%
  dplyr::arrange(desc(Variant))
# save raw data to disc
base::saveRDS(ex, file = here::here("data/editdata", "iceamp_ex.rda"))
# inspect data
head(ex)
```



We have reached the end of part 1 of the analysis.

## Session information{-}

```{r amphkpie_01_71, echo=T, eval = T, message=FALSE, warning=FALSE}
sessionInfo()
```
